Relevance-based Quantization of Scattering Features for Unsupervised Mining of Environmental Audio

### 2018-02-19 paper/structureScene.tex

>>>>

\section*{Availability of data and materials}
The dataset supporting the conclusions of this article is available in the dcase2013 repository,  \sloppy \url{http://c4dm.eecs.qmul.ac.uk/sceneseventschallenge/description.html}.
The software supporting the conclusions of this article is available in
\begin{itemize}
\item Project name: article2017EstimationAmbiance
\item \sloppy Project home page: \url{https://github.com/mathieulagrange/paperRelevanceBasedSimilarity}
\item Programming language: Matlab
\item License: GNU GPL
\item Any restrictions to use by non-academics: license needed
\end{itemize}

\section*{Competing interests}
The authors declare that they have no competing interests.

\section*{Funding}
This study is co-funded by the ANR under project reference ANR-16-CE22-0012.

\section*{Authors' contributions}
GL and VL carried out the numerical experiments and drafted the manuscript. VL, GL, JA and ML participated in the design of the study and helped to draft the manuscript.
All authors read and approved the final manuscript.
